---
title: "Timesheet Summary"
output: slidy_presentation
css: "slidy_presentation_css.css"
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

``` {r NicsDataPrep}

library(readr)
library(ggplot2)

# Import the timesheet data
TimesheetData <- read_csv("TimesheetData.csv", col_types = cols(Date = col_date(format = "%d/%m/%Y"), Month = col_integer(), Week = col_integer(), Year = col_integer()))

# Create a summary of hours by week
HoursByWeek <- aggregate(TimesheetData$Hours, by=list(Category=TimesheetData$Week), FUN=sum)

# Rename the column headings of the HoursByWeek data set to Week and TotalHours
names(HoursByWeek) <- c("Week", "TotalHours")

# Create a summary of hours by person
HoursByPerson <- aggregate(TimesheetData$Hours, by=list(Category=TimesheetData$Person), FUN=sum)

# Rename the column headings of the HoursByPerson data set to Person and TotalHours
names(HoursByPerson) <- c("Person", "TotalHours")

# Create a summary of hours by project
HoursByProject <- aggregate(TimesheetData$Hours, by=list(Category=TimesheetData$Project), FUN=sum)

# Rename the column headings of the HoursByProject data set to Project and TotalHours
names(HoursByProject) <- c("Project", "TotalHours")

```

## What's this presentation about?

This is a summary of some dummy timesheet data to illustrate how the data can be visualised using an interactive presentation using R and Shiny.

The presentation imports a CSV file of the dummy timesheet data, creates a plot for each aspect (week, person, project), a dashboard of the 3 graphs arranged in a grid format, and then an interactive Shiny app allowing the user to change the colours of the bars in a bar chart.

## Total Hours By Week

```{r HoursByWeekPlot, echo=FALSE, message=FALSE, fig.width=6, fig.height=5}

# Create and display a bar chart showing the HoursByWeek data
HoursByWeekPlot <- ggplot(HoursByWeek, aes(x = Week, y = TotalHours)) +
  geom_bar(stat = "identity", fill = "#e1ad46") +
  geom_text(aes(label = TotalHours), vjust = 1.6, color = "white", size = 4.5) +
  # ggtitle("Total Hours By Week") +
  theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=24, hjust=0)) + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  theme(panel.background = element_blank()) +  
  theme(axis.text.y = element_blank(),axis.ticks=element_blank()) + 
  theme(axis.text.x = element_text(size=12, color = "#666666")) +
  theme(axis.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=14)) +
  labs(y = "Total Hours")

HoursByWeekPlot

```

## Total Hours By Person

```{r HoursByPersonPlot, echo=FALSE, message=FALSE, fig.width=6, fig.height=5}

# Create and display a bar chart showing the HoursByPerson data
HoursByPersonPlot <- ggplot(HoursByPerson, aes(x = Person, y = TotalHours)) +
  geom_bar(stat = "identity", fill = "#49a4aa") +
  geom_text(aes(label = TotalHours), vjust = 1.6, color = "white", size = 4.5) +
  # ggtitle("Total Hours By Person") +
  theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=24, hjust=0)) + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  theme(panel.background = element_blank()) +  
  theme(axis.text.y = element_blank(),axis.ticks=element_blank()) + 
  theme(axis.text.x = element_text(size=12, color = "#666666")) +
  theme(axis.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=14)) +
  labs(y = "Total Hours")

HoursByPersonPlot

```

## Total Hours By Project

```{r HoursByProjectPlot, echo=FALSE, message=FALSE, fig.width=6, fig.height=5}

# Create and display a bar chart showing the HoursByProject data
HoursByProjectPlot <- ggplot(HoursByProject, aes(x = Project, y = TotalHours)) +
  geom_bar(stat = "identity", fill = "#dd0244") +
  geom_text(aes(label = TotalHours), vjust = 1.6, color = "white", size = 4.5) +
  # ggtitle("Total Hours By Project") +
  theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=24, hjust=0)) + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  theme(panel.background = element_blank()) +  
  theme(axis.text.y = element_blank(),axis.ticks=element_blank()) + 
  theme(axis.text.x = element_text(size=12, color = "#666666")) +
  theme(axis.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=14)) +
  labs(y = "Total Hours")

HoursByProjectPlot

```

## Dashboard

```{r Dashboard, echo=FALSE, message=FALSE, fig.width=12}
library(gridExtra)

# Display the 3 bar charts on one page in a grid format (2 rows and 2 columns)
grid.arrange(HoursByWeekPlot, HoursByPersonPlot, HoursByProjectPlot, nrow = 2, ncol = 2)

```

## Interactive Chart (Shiny App)

Use the drop down below to change the colour of this chart.

```{r InteractiveProjectPlot_shiny}
library(shiny)
library(ggplot2)

shinyApp(
  ui = fluidPage(
    # Allow the user to choose a colour (hex value) from a drop down.
    selectInput("colour", "Choose a colour", choices = c("#666666", "#e1ad46", "#dd0244")),
    plotOutput("NicsProjectPlot")
  ),
  
  server = function(input, output){
    
    output$NicsProjectPlot <- renderPlot(
    
    # Display a chart showing "Total Hours By Project"" and change the colour of the bars to be the colour chosen by the user
    ggplot(HoursByProject, aes(x = Project, y = TotalHours)) +
  geom_bar(stat = "identity", fill = input$colour) +
  geom_text(aes(label = TotalHours), vjust = 1.6, color = "white", size = 4.5) +
  ggtitle("Total Hours By Project") +
  theme(plot.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=24, hjust=0)) + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  theme(panel.background = element_blank()) +  
  theme(axis.text.y = element_blank(),axis.ticks=element_blank()) + 
  theme(axis.text.x = element_text(size=12, color = "#666666")) +
  theme(axis.title = element_text(family = "Trebuchet MS", color="#666666", face="bold", size=14)) +
  labs(y = "Total Hours")
    
    )
  }
)
```